---
title: "Zia's data"
author: "Andrew"
date: "2023-02-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
mydata <- read.csv(file="Zias data.csv")
mydata$Scorpion_ID <- as.factor(mydata$Scorpion_ID)
```

#   Analysis of NumProbes
```{r} 
boxplot(NumProbes~Scorpion_ID,data=mydata)
```

According to the plot, the box labelled "Low" is placed higher on the plot than "High." NumProbes represents the amount of times the scorpions were poked before they were agitated. Scorpions placed in higher temperature were more prone to sting than those placed in lower temperature.

```{r}
favstats(NumProbes~Scorpion_ID,data=mydata)
```
The average amount of probes from scorpions placed in higher temperatures is 6.5. The average amount of probes from scorpions placed in lower temperatures is 23.5. Scorpions in lower temperature were less prone to sting compared to those in higher temperature.

```{r}
t.test(NumProbes~Scorpion_ID,data=mydata)
```
At 95% confidence level, there appears to be a difference between the scorpions placed in higher temperature and lower temperature. Below 95% confidence levels, there is no difference between the scorpions.


#   Analysis of TimeSting
```{r} 
boxplot(TimeSting~Scorpion_ID,data=mydata)
```

According to the plot, it took the scorpions placed in lower temperature more amount of time to sting compared to those placed in higher temperature. We are able to determine this by the placement of the two boxes. The box labelled "high" is smaller than the box labelled "low."

```{r}
favstats(TimeSting~Scorpion_ID,data=mydata)
```

The scorpions placed in higher temperature took less time to sting compared to those in lower temperature. There's a difference in the mean, the standard deviation, and the median for scorpions in higher temperatures than the lower temperature ones in the numerical results.

```{r}
t.test(TimeSting~Scorpion_ID,data=mydata,conf.level=.99)
```
At the 90% confidence level, we can conclude that there is a difference between scorpions placed in lower and higher temperature. However, at 95% and 99% confidence levels, there is no difference between the scorpions.

